SHARP - II: Revealing a bias in observational measurements of dark matter substructure with gravitational lens flux ratios

### 2015-09-11 papers/B1555_EdgeOn/B1555_letter.tex
update of typo

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Beware the effect of edge-on discs]{SHARP - II. Beware the effect of edge-on discs when interpreting the anomalous flux-ratios of gravitationally lensed quasars}
\author[Hsueh et al.]{J.-W. Hsueh,$^{1}$\thanks{E-mail: jwhsueh@ucdavis.edu} C. D. Fassnacht,$^{1}$ S. Vegetti,$^{2}$  J. McKean,$^{3,4}$ C. Spingola,$^{4}$ M. W. Auger,$^{5}$
\newauthor  L. V. E. Koopmans,$^{4}$ and D. J. Lagattuta$^{6}$\\
$^{1}$Department of Physics, University of California, Davis, 1 Shields Ave. Davis, CA 95616, USA\\
$^{2}$Max Planck Institute for Astrophysics, Karl-Schwarzschild-Strasse 1, D-85740 Garching, Germany\\
$^{3}$Netherlands Institute for Radio Astronomy (ASTRON), P.O. Box 2, 7990 AA Dwingeloo, The Netherlands\\
$^{4}$Kapteyn Astronomical Institute, University of Groningen, P.O. Box 800, 9700 AV Groningen, The Netherlands\\
$^{5}$Institute of Astronomy, Madingley Road, Cambridge CB3 0HA, UK\\
$^{6}$University of Lyon, 92 Rue Pasteur, 69007 Lyon, France}
\begin{document}

@@

B1555+375 was observed with the 10 telescopes of the VLBA at a central observing frequency of 1.66 GHz on 2000 March 21 (BN0009; PI: Norbury). The data were recorded at 128 Mbits~s$^{-1}$ and then correlated to produce two spectral windows with 8 MHz bandwidth, 16 channels and both circular polarizations (RR and LL). The observations were phase referenced using J1544+398 every 3 min over the total observing time of 3 h. The data were reduced in the standard manner using the {\sc vlbaprocs} analysis pipeline that is part of the Astronomical Image Processing Software (AIPS). Imaging was done with the {\sc clean} algorithm in AIPS using natural weighting of the visibilities, and restored using an elliptical beam of size $9.7 \times 6.9$~mas at a position angle of $-7.6^\circ$ east of north. The final map (also shown in Fig.~\ref{fig:merlin}) has an rms of 78~$\mu$Jy~beam$^{-1}$.

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Beware the effect of edge-on discs]{SHARP - II: Revealing a bias in observational measurements of dark matter substructure with gravitational lens flux ratios}
\author[Hsueh et al.]{J.-W. Hsueh,$^{1}$\thanks{E-mail: jwhsueh@ucdavis.edu} C. D. Fassnacht,$^{1}$ S. Vegetti,$^{2}$  J. McKean,$^{3,4}$ C. Spingola,$^{4}$ M. W. Auger,$^{5}$
\newauthor  L. V. E. Koopmans,$^{4}$ and D. J. Lagattuta$^{6}$\\
$^{1}$Department of Physics, University of California, Davis, 1 Shields Ave. Davis, CA 95616, USA\\
$^{2}$Max Planck Institute for Astrophysics, Karl-Schwarzschild-Strasse 1, D-85740 Garching, Germany\\
$^{3}$Netherlands Institute for Radio Astronomy (ASTRON), P.O. Box 2, 7990 AA Dwingeloo, The Netherlands\\
$^{4}$Kapteyn Astronomical Institute, University of Groningen, P.O. Box 800, 9700 AV Groningen, The Netherlands\\
$^{5}$Institute of Astronomy, Madingley Road, Cambridge CB3 0HA, UK\\
$^{6}$University of Lyon, 92 Rue Pasteur, 69007 Lyon, France}
\begin{document}

@@

B1555+375 was observed with the 10 telescopes of the VLBA at a central observing frequency of 1.66 GHz on 2000 March 21 (BN0009; PI: Norbury). The data were recorded at 128 Mbits~s$^{-1}$ and then correlated to produce two spectral windows with 8 MHz bandwidth, 16 channels and both circular polarizations (RR and LL). The observations were phase referenced using J1544+398 every 3 min over the total observing time of 3 h. The data were reduced in the standard manner using the {\sc vlbautlis} analysis pipeline that is part of the Astronomical Image Processing Software (AIPS). Imaging was done with the {\sc clean} algorithm in AIPS using natural weighting of the visibilities, and restored using an elliptical beam of size $9.7 \times 6.9$~mas at a position angle of $-7.6^\circ$ east of north. The final map (also shown in Fig.~\ref{fig:merlin}) has an rms of 78~$\mu$Jy~beam$^{-1}$.
